A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-11-21 paper.tex
Fixed typos

% Outline
Section~\ref{sec:ltc} provides some background on the LTC algorithm, 
and formalizes the description initially proposed 
in~\cite{schoellhammer2004lightweight}. Section~\ref{sec:extension} 
presents our norm-independent extension to dimension $n$, and 
Section~\ref{sec:implementation} describes our implementation. 
Section~\ref{sec:results} reports on experiments to validate our 
implementation, and evaluate the impact of n-dimensional LTC on 
energy consumption of connected objects.

@@

To choose between the multidimensional implementation and multiple 
unidimensional ones, we recommend to check whether the desired 
error bound is expressed independently for every sensor, or as an aggregate error between them.
The multidimensional version is
more appropriate for multidimensional sensors, for instance 3D 
accelerometers or 3D gyroscopes, and the multiple unidimensional 
version to be more suitable for multiple independent sensors, for 
instance a temperature and a pressure sensor.
%~ For instance, in case of a 3D accelerometer, if the error 
%~ is expressed simply as 
%~ ``10~mg", then the multidimensional version should be chosen because it 
%~ will guarantee that the norm of the 3D acceleration vector will be 
%~ reconstructed with an error less than 10~mg. Conversely, if the error is 
%~ specified as ``10~mg in x, 
%~ 10~mg in y and 10~mg in z", then the multiple unidimensional version 
%~ should be used.

@@

%\todo{(Put a picture of Neblina in a box worn 
%on the wrist)}
\begin{wrapfigure}{R}{3cm}
\includegraphics[width=3cm]{figures/neblina-wrist.png}
\caption{Setup with Neblina.}
\label{fig:neblina-wrist}
\end{wrapfigure}
We validated the behaviour of our LTC extension on a PC using data 
acquired with Neblina. We collected two 3D accelerometer time-series, a 
short one and a longer one, acquired on two different subjects 
performing biceps curl, with a 50~Hz sampling rate (see 
Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longer 
time-series also has a higher amplitude, perhaps due to differences between 
subjects.

>>>>

% Outline
Section~\ref{sec:ltc} provides some background on the LTC algorithm, 
and formalizes the description initially proposed 
in~\cite{schoellhammer2004lightweight}. Section~\ref{sec:extension} 
presents our norm-independent extension to dimension $n$, and 
Section~\ref{sec:implementation} describes our implementation. 
Section~\ref{sec:results} reports on experiments to validate our 
implementation, and evaluates the impact of n-dimensional LTC on 
energy consumption of connected objects.

@@

To choose between the multidimensional implementation and multiple 
unidimensional ones, we recommend to check whether the desired 
error bound is expressed independently for every sensor, or as an aggregate error between them.
The multidimensional version is
more appropriate for multidimensional sensors, for instance 3D 
accelerometers or 3D gyroscopes, and the multiple unidimensional 
version is more suitable for multiple independent sensors, for 
instance a temperature and a pressure sensor.
%~ For instance, in case of a 3D accelerometer, if the error 
%~ is expressed simply as 
%~ ``10~mg", then the multidimensional version should be chosen because it 
%~ will guarantee that the norm of the 3D acceleration vector will be 
%~ reconstructed with an error less than 10~mg. Conversely, if the error is 
%~ specified as ``10~mg in x, 
%~ 10~mg in y and 10~mg in z", then the multiple unidimensional version 
%~ should be used.

@@

%\todo{(Put a picture of Neblina in a box worn 
%on the wrist)}
\begin{wrapfigure}{R}{3cm}
\includegraphics[width=3cm]{figures/neblina-wrist.png}
\caption{Setup with Neblina.}
\label{fig:neblina-wrist}
\end{wrapfigure}
We validated the behaviour of our LTC extension on a PC using data 
acquired with Neblina. We collected two 3D accelerometer time-series, a 
short one and a longer one, acquired on two different subjects 
performing biceps curl, with a 50~Hz sampling rate (see 
Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longest
time-series also has a higher amplitude, perhaps due to differences between 
subjects.
